Probabilistic Programming around Gaussian Processes

### 2019-10-19 abstract/paper.tex
in progress

\begin{abstract}
	We present GoGP, a library for probabilistic programming around
	Gaussian processes. Kernels, beliefs about hyperparameters
	and about observation inputs and outputs are
	programmatically expressed using the same differentiable
	probabilistic programming framework. One one hand, a basic
	usage with maximum-likelihood hyperparameter estimates and
	homoscedastic Gaussian noise requires as little coding as
	with any Gaussian process library. On the other hand,
	imposing prior beliefs on hyperparameters, handling input
	uncertainty, heteroscedastic and non-Gaussian noise, or
	change point detection can be organically added on top of a
	Gaussian process kernel. Just like distributions in
	probabilistic programs, kernels can be flexibly combined
	using general code flow rather than through predefined
	combination operators (usually addition and multiplication).
	Implemented in Go, a general-purpose programming language 
	popular for server-side programming, our library is well
	suited for integration into data processing/machine learning
	pipelines.  We demonstrate different uses of the library on
	a variety of case studies inspired by applications.
\end{abstract}

>>>>

\begin{abstract}
	We present GoGP, a library for probabilistic programming
	around Gaussian processes. Kernels, beliefs about
	hyperparameters and about observation inputs and outputs are
	programmatically expressed using the same differentiable
	probabilistic programming framework. One one hand, a basic
	usage with maximum-likelihood hyperparameter estimates and
	homoscedastic Gaussian noise requires as little coding as
	with any Gaussian process library. On the other hand,
	imposing prior beliefs on hyperparameters, handling input
	uncertainty, heteroscedastic and non-Gaussian noise, or
	change point detection can be organically added on top of a
	Gaussian process kernel. Just like distributions in
	probabilistic programs, kernels can be flexibly combined
	using general code flow rather than through predefined
	combination operators (usually addition and multiplication).
	Implemented in Go, a general-purpose programming language
	popular for server-side programming, our library is both
	well suited for integration into data processing/machine
	learning pipelines and exploits language features such as
	efficient light-weight computation parallelism for
	computation efficiency.  We demonstrate different uses of
	the library on a variety of case studies inspired by
	applications. 
\end{abstract}
